---
title: "Met RMSD Survival analysis"
author: "Girish Tillu, Ashwini Mathur, Vinay Mahajan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    df_print: default
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(survival)
library(survminer)
library(data.table)
library(ggplot2)
library(dplyr)
library(anytime)
library(knitr)
library(DT)

#source("D:/Hospital_data/ProgresSQL/prgm/090_adsl_analysis_survival_macrocall_creation.R")

source("D:/Hospital_data/ProgresSQL/prgm/08_nonoverlap.R")

```

```{r, include=FALSE}

mcall <- data.table (unique(disease [grepl (paste("^RMSD", sep=""), Code), c("Code"), ])) [order(Code)]
mcall0 <- mcall [, z:=1]

unqpat <- data.table( unique( all_met_rmsd [RMSD == 1, c("mr_no", "patient_gender", "vismon", "Metabolic", "RMSD"), ]))
unqpat <- unqpat [, z:=1]
unqpat02 <- merge(unqpat, mcall0 [, c("z", "Code"),], allow.cartesian = TRUE, by = c("z"))

disease0 <- merge (x = disease [, c("mr_no", "Code", "idurmonth"), ], 
                   y = unqpat02,
                   by = c("mr_no", "Code"),
                   all.y = TRUE,
                   all.x = TRUE)
disease0 <- disease0 [, disdur := ifelse(is.na(idurmonth), vismon, idurmonth), ]
disease0 <- disease0 [, status := ifelse(is.na(idurmonth), 0, 1 )]

```

# RMSD : A2.0 Aamavaata
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : A2.0 Aamavaata'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : A2.0 Aamavaata");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : A2.1 Aamavaata - Kaphaja
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : A2.1 Aamavaata - Kaphaja'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : A2.1 Aamavaata - Kaphaja");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : A2.2 Aamavaata - Pittaja
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : A2.2 Aamavaata - Pittaja'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : A2.2 Aamavaata - Pittaja");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : A2.3 Aamavaata - Vaataja
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : A2.3 Aamavaata - Vaataja'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : A2.3 Aamavaata - Vaataja");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : A3.0 Abhighataja Shoola
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : A3.0 Abhighataja Shoola'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : A3.0 Abhighataja Shoola");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S10.0 Stambha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S10.0 Stambha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S10.0 Stambha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S10.1 Stambha - Baahu Stambha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S10.1 Stambha - Baahu Stambha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S10.1 Stambha - Baahu Stambha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S10.10 Stambha - Prishtha Stambha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S10.10 Stambha - Prishtha Stambha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S10.10 Stambha - Prishtha Stambha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S10.12 Stambha - Sandhi Stambha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S10.12 Stambha - Sandhi Stambha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S10.12 Stambha - Sandhi Stambha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S10.13 Stambha - Siraa Stambha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S10.13 Stambha - Siraa Stambha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S10.13 Stambha - Siraa Stambha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S10.14 Stambha - Uru Stambha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S10.14 Stambha - Uru Stambha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S10.14 Stambha - Uru Stambha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S10.4 Stambha - Greevaa Stambha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S10.4 Stambha - Greevaa Stambha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S10.4 Stambha - Greevaa Stambha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S10.5 Stambha - Hanu Stambha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S10.5 Stambha - Hanu Stambha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S10.5 Stambha - Hanu Stambha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S10.6 Stambha - Hridaya Stambha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S10.6 Stambha - Hridaya Stambha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S10.6 Stambha - Hridaya Stambha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.0 Sthaanabhedena Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.0 Sthaanabhedena Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.0 Sthaanabhedena Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.1 Sthaanabhedena Graha - Anga Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.1 Sthaanabhedena Graha - Anga Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.1 Sthaanabhedena Graha - Anga Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.11 Sthaanabhedena Graha - Katee Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.11 Sthaanabhedena Graha - Katee Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.11 Sthaanabhedena Graha - Katee Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.13 Sthaanabhedena Graha - Manyaa Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.13 Sthaanabhedena Graha - Manyaa Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.13 Sthaanabhedena Graha - Manyaa Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.14 Sthaanabhedena Graha - Marma Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.14 Sthaanabhedena Graha - Marma Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.14 Sthaanabhedena Graha - Marma Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.17 Sthaanabhedena Graha - Paada Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.17 Sthaanabhedena Graha - Paada Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.17 Sthaanabhedena Graha - Paada Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.18 Sthaanabhedena Graha - Paarshva Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.18 Sthaanabhedena Graha - Paarshva Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.18 Sthaanabhedena Graha - Paarshva Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.19 Sthaanabhedena Graha - Prishtha Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.19 Sthaanabhedena Graha - Prishtha Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.19 Sthaanabhedena Graha - Prishtha Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.20 Sthaanabhedena Graha - Shiro Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.20 Sthaanabhedena Graha - Shiro Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.20 Sthaanabhedena Graha - Shiro Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.22 Sthaanabhedena Graha - Uro Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.22 Sthaanabhedena Graha - Uro Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.22 Sthaanabhedena Graha - Uro Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.23 Sthaanabhedena Graha - Vaak Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.23 Sthaanabhedena Graha - Vaak Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.23 Sthaanabhedena Graha - Vaak Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.3 Sthaanabhedena Graha - Gala Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.3 Sthaanabhedena Graha - Gala Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.3 Sthaanabhedena Graha - Gala Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.5 Sthaanabhedena Graha - Hanu Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.5 Sthaanabhedena Graha - Hanu Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.5 Sthaanabhedena Graha - Hanu Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.6 Sthaanabhedena Graha - Hrid Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.6 Sthaanabhedena Graha - Hrid Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.6 Sthaanabhedena Graha - Hrid Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.7 Sthaanabhedena Graha - Jaanugraha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.7 Sthaanabhedena Graha - Jaanugraha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.7 Sthaanabhedena Graha - Jaanugraha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# RMSD : S13.8 Sthaanabhedena Graha - Janghaa Graha
```{r, echo = FALSE}
tmp <- disease0 [RMSD== 1 & patient_gender != '' & Code =='RMSD : S13.8 Sthaanabhedena Graha - Janghaa Graha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="RMSD : S13.8 Sthaanabhedena Graha - Janghaa Graha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```
