---
title: "Met RMSD analysis"
author: "Girish Tillu, Ashwini Mathur, Vinay Mahajan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(ggplot2)
library(dplyr)
library(anytime)
library(knitr)
library(DT)

all_met_rmsd <- readRDS("D:/Hospital_data/ProgresSQL/analysis/01adsl_met_rmsd.rds")

all_met_rmsd <- all_met_rmsd [, `:=` (baseage = min(age)), by =.(mr_no)]
all_met_rmsd <- all_met_rmsd [, `:=` (vismon = round( cdur/30.4375, digits = 0))]

# Baseline age
age01 <- unique( all_met_rmsd [, c("mr_no", "baseage", "combine", "RMSD", "Metabolic", "patient_gender")] )

# Age by visits
age011 <- unique( all_met_rmsd [, c("mr_no", "age", "combine", "RMSD", "Metabolic", "patient_gender", "vis")] )

tbl0001 <- all_met_rmsd [, .(NoofPat = uniqueN(mr_no)), by = .(combine)]
tbl0002 <- all_met_rmsd [, .(NoofPat = uniqueN(mr_no)), by = .(combine, patient_gender)]

tbl0002t <- dcast(data = tbl0002, 
                  combine ~ patient_gender, 
                  subset = .(patient_gender != ""),
                  value.var = "NoofPat")


tbl0003 <- all_met_rmsd [ Metabolic == 1, .(Metabolic = uniqueN(mr_no))]
tbl0004 <- all_met_rmsd [ RMSD == 1, .(RMSD = uniqueN(mr_no))]

```

```{r, include=FALSE}

# Create unique patient records for metabolic patients
met_unq <- unique(all_met_rmsd [ Metabolic ==1 , c("mr_no", "patient_gender", "cdur", "all_ip", "all_op", "all_vis")])
met_unq0 <- melt(data =met_unq, 
                 id.vars = c("mr_no", "patient_gender"),
                 measure.vars = c("cdur", "all_ip", "all_op", "all_vis")) 
met_unq_0=copy(met_unq0)

met_unq1 <- met_unq_0 [, patient_gender := "-Total",]
met_all <- rbind(met_unq0, met_unq1)


# Create unique patient records for RMSD patients
rmsd_unq <- unique(all_met_rmsd [ RMSD ==1 , c("mr_no", "patient_gender", "cdur", "all_ip", "all_op", "all_vis")])
rmsd_unq0 <- melt(rmsd_unq, 
                 id.vars = c("mr_no", "patient_gender"),
                 measure.vars = c("cdur", "all_ip", "all_op", "all_vis")) 

rmsd_unq_0 <- copy(rmsd_unq0)
rmsd_unq1 <- rmsd_unq_0 [, patient_gender := "-Total",]
rmsd_all <- rbind(rmsd_unq0, rmsd_unq1)

summ_stat <- function (datain, xsub, by, by1, dataout ="D8")
{
  stats_data <- datain [, .(n=uniqueN(mr_no), 
                            mean = round( mean(get(xsub), na.rm = TRUE), digits =1),
                            median= round( median(get(xsub), na.rm = TRUE), digits =2),
                            SD = round( sd(get(xsub), na.rm = TRUE), digits =2),
                            min = round( min(get(xsub), na.rm = TRUE), digits =0),
                            max = round( max(get(xsub), na.rm = TRUE), digits =0)), 
                        by = .(get(by), get(by1))]
  
  assign(dataout, stats_data, envir=.GlobalEnv)
}

summ_stat (datain =met_all, xsub = 'value', by =c('variable'), by1 =c("patient_gender"), dataout ="met_stat_gender00")

summ_stat (datain =rmsd_all, xsub = 'value', by =c('variable'), by1 =c("patient_gender"), dataout ="rmsd_stat_gender00")

tbl0001 <- all_met_rmsd [, .(NoofPat = uniqueN(mr_no)), by = .(combine)]
tbl0002 <- all_met_rmsd [, .(NoofPat = uniqueN(mr_no)), by = .(combine, patient_gender)]

tbl0002t <- dcast(data = tbl0002, 
                  combine ~ patient_gender, 
                  subset = .(patient_gender != ""),
                  value.var = "NoofPat")


tbl0003 <- all_met_rmsd [ Metabolic == 1, .(Metabolic = uniqueN(mr_no))]
tbl0004 <- all_met_rmsd [ RMSD == 1, .(RMSD = uniqueN(mr_no))]


# Analysis for the disease duration
dis_data <- unique(all_met_rmsd [, .(disstt = min(anydate( newdt) ), 
                                     disend = max( anydate(newdt)),
                                     disdur = as.numeric(max(anydate(newdt)) - min(anydate(newdt)) + 1)), 
                                 by = .(distype, mr_no, patient_gender, all_vis, all_ip, all_op,  Code, description)] )
dis_data02 <- dis_data[Code !=""]

dis_data02_0 <- copy(dis_data02)
dis_data03 <- dis_data02_0 [, patient_gender := "-Total",]
dis_all <- rbind(dis_data02, dis_data03)
dis_all <- dis_all [, catvar := paste(distype, " ", Code, " ", description), ]

summ_stat (datain =dis_all, xsub = 'disdur', by =c('patient_gender'), by1 =c("catvar"), dataout ="dis_stat_gender00")


summ_stat (datain =age01 [ Metabolic ==1 & baseage > 0], xsub = 'baseage', by =c('Metabolic'), by1 =c("patient_gender"), dataout ="age02met")

summ_stat (datain =age01 [ RMSD ==1 & patient_gender != "" & baseage > 0], xsub = 'baseage', by =c('RMSD'), by1 =c("patient_gender"), dataout ="age02rmsd")

summ_stat (datain =age011 [ Metabolic ==1 & age > 0], xsub = 'age', by =c('vis'), by1 =c("patient_gender"), dataout ="age02vismet")

summ_stat (datain =age011 [ RMSD ==1 & patient_gender != "" & age > 0], xsub = 'age', by =c('vis'), by1 =c("patient_gender"), dataout ="age02visrmsd")

```

# Analysis

Metabolic and RMSD patients, this document contains different analysis

## Disease Category
```{r, echo= FALSE}
kable(tbl0001, col.names = c("Disease category", "Number of patients"), caption= "--") 
```

## Disease category by gender 
```{r, echo= FALSE}
#kable(tbl0002t, col.names = c("Disease category", "Females", "Males"), caption= "--") 
datatable(tbl0002t)
```

## Number of Metabolic patients
```{r, echo= FALSE}
kable(tbl0003, caption = "All Metabolic patients") 

```

## Number of RMSD patients
```{r, echo= FALSE}
kable(tbl0004, caption = "All RMSD patients") 

```

# Summary statistics of age at baseline and subsequent visits
This section covers age related analysis  

## Metabolic: Summary statistics of baseline age in years
```{r, echo= FALSE}
kable(age02met [order(get, get.1)], caption = "--") 

```

## RMSD: Summary statistics of baseline age in years
```{r, echo= FALSE}
kable(age02rmsd [order(get, get.1)], caption = "--") 

```

## Metabolic: Summary statistics of age in years, by visit
```{r, echo= FALSE}
#kable(age02vismet [order(get, get.1)], caption = "--") 

datatable(age02vismet)
```

## RMSD: Summary statistics of age in years, by visit
```{r, echo= FALSE}
#kable(age02visrmsd [order(get, get.1)], caption = "--") 

datatable(age02visrmsd)
```

# Analysis related to number of visits and duration 
## Metabolic: Summary statistics in days and visits
cdur: Total duration of hospital visits,  
all_ip: All IP visits, all_op: All OP visits, all_vis: All IP + OP visits  
```{r, echo= FALSE}
kable(met_stat_gender00 [order(get, get.1)], caption = "--") 

```

## RMSD: Summary statistics in days and visits
cdur: Total duration of hospital visits,  
all_ip: All IP visits, all_op: All OP visits, all_vis: All IP + OP visits
```{r, echo= FALSE}
kable(rmsd_stat_gender00 [order(get, get.1)], caption = "") 

```

## Diseases: Summary statistics in days, by gender
```{r, echo= FALSE}
#kable(dis_stat_gender00 [order(get.1, get)], caption = "--") 

datatable(dis_stat_gender00)
```

# Cumulative analysis:
In this analysis patients are counted multiple times as per available data for each time period  

## Cumulative display of patients by duration
```{r, echo= FALSE, message= FALSE}

source("D:/Hospital_data/ProgresSQL/prgm/07_cumulative_duration.R")

kable(diag100all, caption="--")

```

## Cumulative display of patients by duration and gender
```{r, echo= FALSE, message= FALSE}

datatable(diag100all_g [patient_gender !=""], caption="--")

```

## Cumulative display of patients by Code and duration
```{r, echo= FALSE, message= FALSE}

source("D:/Hospital_data/ProgresSQL/prgm/07_cumulative_dur_byCode.R")

#kable(diag100all [, -c("durlwr")], caption="--")

datatable( diag100all [, -c("durlwr")] )
```


# Non-overlapping analysis

```{r, echo= FALSE, message= FALSE}
source("D:/Hospital_data/ProgresSQL/prgm/07_cumulative_dur_byCode_Part02.R")

```

## Total patients present across different time points 
```{r, echo =FALSE, message=FALSE}

datatable(diag10000all)

```

## Summary statistics of total duration across different time points
```{r, echo =FALSE, message=FALSE}

datatable(nonovr01)

```

## Summary statistics of total visits across different time points
```{r, echo =FALSE, message=FALSE}

datatable(nonovr011)

```

## Summary statistics of total visits across different time points for each disease
```{r, echo =FALSE, message=FALSE}

datatable(nonovr03)

```

```{r, echo= FALSE, message= FALSE}
source("D:/Hospital_data/ProgresSQL/prgm/08_nonoverlap.R")

```

## Total duration across non overlapping time periods
```{r, echo =FALSE, message=FALSE}

datatable (nonovr01)
```

## Metabolic: total duration by gender across non overlapping time periods
```{r, echo =FALSE, message=FALSE}

datatable (nonovr01met)
```

## RMSD: total duration across non overlapping time periods
```{r, echo =FALSE, message=FALSE}

datatable (nonovr01rmsd)
```

## Metabolic: total duration for by gender across non overlapping time periods
```{r, echo =FALSE, message=FALSE}

datatable (nonovr01ovr_met)
```

## Metabolic: total duration for each disease across non overlapping time periods
```{r, echo =FALSE, message=FALSE}

datatable (nonovr01dis_met)
```

## RMSD: total duration for overall by gender non overlapping time periods
```{r, echo =FALSE, message=FALSE}

datatable (nonovr01ovr_rmsd)
```

## RMSD: total duration for each disease across non overlapping time periods
```{r, echo =FALSE, message=FALSE}

datatable (nonovr01dis_rmsd)
```

# No-overlapping time period, frequency counts

## Frequency counts for Total number of patients with treatment and diseases
```{r, echo =FALSE, message=FALSE}

datatable (dis_freq01all)
```

# Diseases present in each non-overlapping duration
If a disease is present at least in a time period once then denote it by Yes 
```{r, echo =FALSE, message=FALSE}
datatable(diag950rpt_t)

```
