---
title: "Metabolic Survival analysis"
author: "Girish Tillu, Ashwini Mathur, Vinay Mahajan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    df_print: default
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(survival)
library(survminer)
library(data.table)
library(ggplot2)
library(dplyr)
library(anytime)
library(knitr)
library(DT)

#source("D:/Hospital_data/ProgresSQL/prgm/090_adsl_analysis_survival_macrocall_creation.R")

source("D:/Hospital_data/ProgresSQL/prgm/08_nonoverlap.R")

```

```{r, include=FALSE}

mcall <- data.table (unique(disease [grepl (paste("^Metabolic", sep=""), Code), c("Code"), ])) [order(Code)]
mcall0 <- mcall [, z:=1]

unqpat <- data.table( unique( all_met_rmsd [Metabolic == 1, c("mr_no", "patient_gender", "vismon", "Metabolic", "RMSD"), ]))
unqpat <- unqpat [, z:=1]
unqpat02 <- merge(unqpat, mcall0 [, c("z", "Code"),], allow.cartesian = TRUE, by = c("z"))

disease0 <- merge (x = disease [, c("mr_no", "Code", "idurmonth"), ], 
                   y = unqpat02,
                   by = c("mr_no", "Code"),
                   all.y = TRUE,
                   all.x = TRUE)
disease0 <- disease0 [, disdur := ifelse(is.na(idurmonth), vismon, idurmonth), ]
disease0 <- disease0 [, status := ifelse(is.na(idurmonth), 0, 1 )]

```

# Metabolic : M10.0 Medoroga
```{r, echo = FALSE}
tmp <- disease0 [Metabolic== 1 & patient_gender != '' & Code =='Metabolic : M10.0 Medoroga'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="Metabolic : M10.0 Medoroga");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# Metabolic : M10.1 Medoroga - Sthula medho roga
```{r, echo = FALSE}
tmp <- disease0 [Metabolic== 1 & patient_gender != '' & Code =='Metabolic : M10.1 Medoroga - Sthula medho roga'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="Metabolic : M10.1 Medoroga - Sthula medho roga");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# Metabolic : M10.2 Medoroga - Sukshma medho roga
```{r, echo = FALSE}
tmp <- disease0 [Metabolic== 1 & patient_gender != '' & Code =='Metabolic : M10.2 Medoroga - Sukshma medho roga'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="Metabolic : M10.2 Medoroga - Sukshma medho roga");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# Metabolic : M2.0 Madhumeha
```{r, echo = FALSE}
tmp <- disease0 [Metabolic== 1 & patient_gender != '' & Code =='Metabolic : M2.0 Madhumeha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="Metabolic : M2.0 Madhumeha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# Metabolic : P5.0 Prameha
```{r, echo = FALSE}
tmp <- disease0 [Metabolic== 1 & patient_gender != '' & Code =='Metabolic : P5.0 Prameha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="Metabolic : P5.0 Prameha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# Metabolic : P5.1 Prameha - Krusha
```{r, echo = FALSE}
tmp <- disease0 [Metabolic== 1 & patient_gender != '' & Code =='Metabolic : P5.1 Prameha - Krusha'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="Metabolic : P5.1 Prameha - Krusha");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# Metabolic : P5.2 Prameha - Pidaka
```{r, echo = FALSE}
tmp <- disease0 [Metabolic== 1 & patient_gender != '' & Code =='Metabolic : P5.2 Prameha - Pidaka'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="Metabolic : P5.2 Prameha - Pidaka");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# Metabolic : P5.3 Prameha - Sthula
```{r, echo = FALSE}
tmp <- disease0 [Metabolic== 1 & patient_gender != '' & Code =='Metabolic : P5.3 Prameha - Sthula'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="Metabolic : P5.3 Prameha - Sthula");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# Metabolic : P5.4 Prameha - Upadrava
```{r, echo = FALSE}
tmp <- disease0 [Metabolic== 1 & patient_gender != '' & Code =='Metabolic : P5.4 Prameha - Upadrava'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="Metabolic : P5.4 Prameha - Upadrava");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```

# Metabolic : S16.0 Sthaulya
```{r, echo = FALSE}
tmp <- disease0 [Metabolic== 1 & patient_gender != '' & Code =='Metabolic : S16.0 Sthaulya'];
km_fit <- survfit(Surv(disdur, status) ~ patient_gender, data= tmp);
p <- ggsurvplot(km_fit, 
           data =tmp, 
           conf.int = TRUE,          # Add confidence interval
           pval = TRUE,              # Add p-value
           pval.method = TRUE,
           risk.table = TRUE,        # Add risk table
           risk.table.height = 0.25, # Useful to change when you have multiple groups
           surv.median.line = "hv",  # add the median survival pointer.
           cumevents = TRUE, 
           add.all = TRUE, 
           title ="Metabolic : S16.0 Sthaulya");

rescox <- coxph(Surv(disdur, status) ~ patient_gender, data= tmp)

```

## Kaplan Meier table
```{r, echo = FALSE}
summary(km_fit, times = durlwr)

```

## Survival plot
```{r, echo = FALSE}
p

```

## Hazard ratio plot
```{r, echo = FALSE}
rescox;ggforest(rescox, data=tmp)

```


